Namespace Tunnels in Content-Centric Networks

### 2017-04-09 paper/06-perf-analysis.tex
paper sec 4.2
Updates
Chris's pass

\section{Discussion and Analysis}\label{sec:analysis}

@@

\subsection{State Consumption}
The CCVPN design has an immediate impact on the FIB and PIT size of a gateway.
(The content store size remains unaffected since only decapsulated content objects
are ever cached.) Let $F_S$ be the total size of a standard forwarder 
FIB in terms of bytes and
$N_F$ be the number of entries in the FIB. For simplicity, we will assume that
each name prefix in the FIB has a constant size of $64$B. In practice we expect
this to be a comfortable upper bound. Thus, $F_S = N_Fs$, where $s$ is the size of
each FIB entry. Here, $s$ includes a name prefix (of size $64$B) and a bit vector
that identifies the matching links for the interface. We assume that a gateway has
$128$ links which, again, is a comfortable upper bound. Therefore, $F_S = 80N_F$B.
Now consider the FIB size $F_G$ for a CCVPN gateway. Some entries in these FIBs will
point to ``private'' prefixes, i.e., other domains, and therefore have a larger size
to account for the corresponding prefix and key material that must be stored. 
For both public- and symmetric-key encryption, the key size is the same: $32$B \cite{sodium}. 
Therefore, by taking into account two both the FIB entry prefix key, translation
prefix, encryption key, and corresponding bit vector, the total size of one ``private''
FIB entry will be $176$B, meaning that $F_G = 176N_F$B. By comparing $F_S$ to $F_G$, we 
see that, in the worst case, the CCVPN FIB is at most $F_G/F_S = 176/80 = 2.2$ times larger
than the standard FIB. In practice, however, we expect this to be much smaller, since the
fraction of public to private FIB entries in a gateway will be non-zero.

We will now apply the same analysis to the PIT size. A standard PIT entry includes a 
complete name and ingress bit vector. (They may also include the optional {\tt KeyId}
and {\tt ContentId}, but since they are included in the gateway PIT as well we omit them
from this analysis.) A gateway PIT entry will contain the same elements of a standard
PIT entry but also a symmetric encryption key ($32$B), nonce ($12$B), and an 
encapsulation name ($64$B + $32$B).
The encapsulation name is the name of an encapsulated interest and includes an additional
$32$B {\tt PayloadID} segment to identify the encapsulated value in the payload. Let 
$P_S$ and $P_G$ be the sizes of the standard and gateway PIT, respectively, and let $N_P$ 
be the number of PIT entries in one such table. Based on the above discussion, and assuming
again that a name is at most $64$B, a standard PIT entry is of the size $80$B. In contrast,
a gateway PIT entry is of size $204$B. Therefore, in the worst case, the CCVPN PIT
will be at most $P_G / P_S = 204/80 = 2.55$B larger than the standard PIT. Assuming 
a steady state size of approximately $1e^5$ entries \cite{carofiglio2015pending}, 
this means that the PIT will be $20.4$MB, which is well within the capacity of 
modern memory systems.

@@

Another performance deficiency comes from the fact that gateways cannot process packets
without allocating memory. Specifically, since each packet requires either an encryption
or decryption, which cannot be done entirely in-place, the gateway must allocate some amount
of memory for every processed packet. This overhead can outweigh the cryptographic computations
if the packet arrival rate is high enough. Therefore, when implementing CCVPN, special care
must be taken to ensure that all cryptographic operations are performed in-place where possible.

>>>>

\section{Performance Analysis}\label{sec:analysis}

@@

\subsection{State Consumption}
The CCVPN design has an immediate impact on the FIB and PIT size of a gateway.
(The content store size remains unaffected since only decapsulated content objects
are ever cached.) Let $F_S$ be the total size of a standard forwarder
FIB in terms of bytes and
$N_F$ be the number of entries in the FIB. For simplicity, we will assume that
each name prefix in the FIB has a constant size of $64$B. In practice we expect
this to be a comfortable upper bound. Thus, $F_S = N_Fs$, where $s$ is the size of
each FIB entry. Here, $s$ includes a name prefix (of size $64$B) and a bit vector
that identifies the matching links for the interface. We assume that a gateway has
$128$ links which, again, is a comfortable upper bound. Therefore, $F_S = 80N_F$B.
Now consider the FIB size $F_G$ for a CCVPN gateway. Some entries in these FIBs will
point to ``private'' prefixes, i.e., other domains, and therefore have a larger size
to account for the corresponding prefix and key material that must be stored.
For both public- and symmetric-key encryption, the key size is the same: $32$B \cite{sodiumGithub}.
Therefore, by taking into account two both the FIB entry prefix key, translation
prefix, encryption key, and corresponding bit vector, the total size of one ``private''
FIB entry will be $176$B, meaning that $F_G = 176N_F$B. By comparing $F_S$ to $F_G$, we
see that, in the worst case, the CCVPN FIB is at most $F_G/F_S = 176/80 = 2.2$ times larger
than the standard FIB. In practice, however, we expect this to be much smaller, since the
fraction of public to private FIB entries in a gateway will be non-zero.

We will now apply the same analysis to the PIT size. A standard PIT entry includes a
complete name and ingress bit vector. (They may also include the optional {\tt KeyId}
and {\tt ContentId}, but since they are included in the gateway PIT as well we omit them
from this analysis.) A gateway PIT entry will contain the same elements of a standard
PIT entry but also a symmetric encryption key ($32$B), nonce ($12$B), and an
encapsulation name ($64$B + $32$B).
The encapsulation name is the name of an encapsulated interest and includes an additional
$32$B {\tt PayloadID} segment to identify the encapsulated value in the payload. Let
$P_S$ and $P_G$ be the sizes of the standard and gateway PIT, respectively, and let $N_P$
be the number of PIT entries in one such table. Based on the above discussion, and assuming
again that a name is at most $64$B, a standard PIT entry is of the size $80$B. In contrast,
a gateway PIT entry is of size $204$B. Therefore, in the worst case, the CCVPN PIT
will be at most $P_G / P_S = 204/80 = 2.55$B larger than the standard PIT. Assuming
a steady state size of approximately $1e^5$ entries \cite{carofiglio2015pending},
this means that the PIT will be $20.4$MB, which is well within the capacity of
modern systems.

@@

Another performance deficiency comes from the fact that gateways cannot process packets
without allocating memory. Specifically, each packet requires either an encryption
or decryption. However, this cannot be done entirely in-place, the gateway must allocate some amount
of memory for every processed packet, e.g., to store the MAC tag, to account for
ciphertext expansion, or to apply padding, if desired. This overhead can outweigh
the cryptographic computations if the packet arrival rate is high enough. Therefore,
when implementing CCVPN, special care must be taken to ensure that memory allocations
are minimized or avoided where possible.

### 2017-04-09 paper/07-experiment.tex
Chris's pass

\begin{itemize}
 \item \textbf{One consumer and one producer $[1,1]$}: We use this setting, with only one consumer and one producer, to slowly increase the interest issuance rate until we are able to determine the maximum network throughput and the impact on RTT as congestion increases.
 \item \textbf{Multiple consumers and one producer $[M,1]$}: In this setting we fix the interest issuance rate so that each consumer requests approximately 1 mbps of data, and we gradually increase the number of consumers in the network, until the throughput per consumer starts to decrease, i.e., until congestion starts to occur. In this setting, the interests coming from all consumers are served by a single producer.  
 \item \textbf{Multiple consumers and multiple producers $[M,N]$}: In this experiment we also gradually increase the number consumers, but we increase the number of producers by the same amount at each round, i.e., $M=N$. The number of hosts (consumers and producers) is increased until congestion is observed.
\end{itemize}

@@

Fig.~\ref{exp1} shows the the network performance when $[M,N]=[1,1]$ as the consumer's request rate increases. The network achieves a maximum throughput of 100 mbps in the PKE version and a
slightly higher throughput of 110 mbps in the symmetric key version. Conversely, the average RTT per message starts to increase as the interest issuance rate approaches the maximum network throughput, as a signal of congestion in the routers.

The results for multiple consumers requesting to a single producer ($[M,1]$) are depicted in Fig.~\ref{exp2}.
In this setting, each consumer receives close to the requested throughput (1 mbps) when less than 50 clients are requesting contents at the same time.
With more than 60 clients the Avg. RTT starts to increase due to congestion, and the average throughput experienced by each client is gradually reduced.

Since in CCN the consumer signs every content, the congestion presented in Fig.~\ref{exp2} might be influenced by the overhead of having a single producer signing an enormous number of interests, in addition to the gateways' cryptographic overhead.
To evaluate that effect in Fig.~\ref{exp3}, we show the average throughput and RTT in the scenario with $[M,N]$ consumers and producers, where $M=N$ and each consumer requests from a specific producer.
In such scenario, we see that the results are slightly better. The network offers the requested throughput (1 mbps per client) with up to 60 nodes, in PKE mode, and 70 nodes, in symmetric key mode.

>>>>

\begin{itemize}
 \item \textbf{One consumer and one producer $[1,1]$}: We use this setting, with
 only one consumer and one producer, to slowly increase the interest issuance
 rate until we are able to determine the maximum network throughput and the
 impact on RTT as congestion increases.
 \item \textbf{Multiple consumers and one producer $[M,1]$}: In this setting we
 fix the interest issuance rate so that each consumer requests approximately $1$
 mbps of data, and we gradually increase the number of consumers in the network,
 until the throughput per consumer starts to decrease, i.e., until congestion
 starts to occur. In this setting, the interests coming from all consumers are
 served by a single producer.
 \item \textbf{Multiple consumers and multiple producers $[M,N]$}: In this experiment
 we also gradually increase the number consumers, but we increase the number of
 producers by the same amount at each round, i.e., $M=N$. The number of hosts
 (consumers and producers) is increased until congestion is observed.
\end{itemize}

@@

Fig.~\ref{exp1} shows the the network performance when $[M,N]=[1,1]$ as the
consumer's request rate increases. The network achieves a maximum throughput of
$100$ mbps in the PKE version and a slightly higher throughput of $110$ mbps in
the symmetric key version. Conversely, the average RTT per message starts to
increase as the interest issuance rate approaches the maximum network throughput,
as a signal of congestion in the routers.

The results for multiple consumers requesting to a single producer ($[M,1]$) are
depicted in Fig.~\ref{exp2}. In this setting, each consumer receives close to the
requested throughput ($1$ mbps) when less than $50$ clients are requesting contents at
the same time. With more than $60$ clients the Avg. RTT starts to increase due to
congestion, and the average throughput experienced by each client is gradually reduced.

Since in CCN the consumer signs every content, the congestion presented in
Fig.~\ref{exp2} might be influenced by the overhead of having a single producer
signing an enormous number of interests, in addition to the gateways' cryptographic overhead.
To evaluate that effect in Fig.~\ref{exp3}, we show the average throughput and RTT
in the scenario with $[M,N]$ consumers and producers, where $M=N$ and each consumer
requests from a specific producer. In such scenario, we see that the results are
slightly better. The network offers the requested throughput ($1$ mbps per client)
with up to $60$ nodes, in PKE mode, and $70$ nodes, in symmetric key mode.

### 2017-04-09 paper/ccvpn.tex
ivan's pass done
Updates
Chris's pass

\usepackage{algorithm2e}
\usepackage{algorithm,algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

@@

\title{Tunnels to Towers: Secure Virtual Private Networking for CCN}

>>>>

\usepackage{algorithm2e}
% \usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\newcommand\adv{$\mathcal{A}$}

@@

\title{Namespace Tunnels in Content-Centric Networks}

\author{
\IEEEauthorblockN{Ivan Oliviera Nunes, Gene Tsudik, Christopher A. Wood$^+$ \thanks{$^+$Supported by the NSF Graduate Research Fellowship DGE-1321846.}}
\IEEEauthorblockA{University of California Irvine \\
\{inunes, gene.tsudik, woodc1\}@uci.edu}
}
